HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
edits to annotation section

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural. The labels assigned to such nodes reflect the extent to which
the relation between the sub-units is preserved in $t$.
For instance, a Scene unit represents the relation between the
Scene elements, such as the predicate (main relation), participants and adverbials.
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong.
We use a three label system with atomic units, as
opposed to a two label one in structural units,
as lexical units often have slight errors, in which cases we do want to provide partial credit.

@@

\begin{compactitem}
\item The components of the translation are ordered differently from the source,
  such that the relation between them changes. For instance, where
  the sentence ``man bites dog'' is translated into a sentence meaning ``dog bites man'',
  the semantic unit corresponding to the Scene will be marked as Bad, while
  the individual atomic units ``dog'', ``bites'' and ``man'' will be marked as Green.
\item A superfluous word or phrase has been inserted into
  the translation. For instance, if ``dog bites man'' is translated into ``dog visciously bites man''.
\item One of the sub-units is missing from the translation.
  For instance, if ``dog bites man'' is translated into ``dog bites''.
\end{compactitem}

@@

An example HUME annotation is given in \figref{fig:hume_tree},
which presents an annotation of a UCCA tree, and a corresponding translation.
We see that ``became a passion'' is deemed atomic, as it is translated as a single unit
in $t$, and thus its sub-units, ``became'', ``a'' and ``passion'' are not evaluated
individually.

>>>>

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural. The labels assigned to such nodes reflect the extent to which
the relation between the sub-units is preserved in $t$.
For instance, a Scene unit represents the relation between the
Scene elements, such as the predicate (main relation), participants and adverbials.
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong.
We use a three label system with atomic units, as
opposed to a two label one in structural units,
as atomic units often have slight errors, in which cases we do want to provide partial credit.

@@

\begin{compactitem}
\item The components of the translation are ordered differently from the source,
  such that the relation between them changes. For instance, where
  the sentence ``man bites dog'' is translated into a sentence meaning ``dog bites man'',
  the semantic unit corresponding to the Scene will be marked as Bad, while
  the individual atomic units ``dog'', ``bites'' and ``man'' will be marked as Green.
\item A superfluous word or phrase has been inserted into
  the translation. For instance, if ``dog bites man'' is translated into ``dog viciously bites man''.
\item One of the sub-units is missing from the translation.
  For instance, if ``dog bites man'' is translated into ``dog bites''. \bh{Note that in this case we also 
  get an error in the atomic unit, assuming that ``man'' is a semantic unit in the source, but for the other
  two cases there is no atomic unit error.}
\end{compactitem}

@@

An example HUME annotation is given in \figref{fig:hume_tree},
which presents an annotation of an UCCA tree, and a corresponding translation.
We see that ``became a passion'' is deemed atomic, as it is translated as a single unit
in $t$, and thus its sub-units, ``became'', ``a'' and ``passion'' are not evaluated
individually.
